---
title: "K-Means Clustering"
output: html_notebook
---
Instalamos los paquetes
```{r}
install.packages("cluster")
install.packages("rattle")
install.packages("NbClust")
install.packages("tidyverse")
install.packages("dplyr")
install.packages("ggplot2")
```
Inicializo las librerias
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(cluster)
library(rattle)
library(NbClust)
```
Leemos el DF
```{r}
df_1 = read.csv('diabetes.csv')
dim =dim(df_1)
```
Preprocesamiento--cambio las columnas chr por columnas int, asignando un valor a cada una y lo escalamos
```{r}
df_aux <-scale(df_1)
df_aux
```

Usamos la libreria NbClust para obtener el numero potencial de clusters
```{r}
set.seed(1234)
nc <- NbClust(df_aux,min.nc = 2,max.nc = 15,method = "kmeans")
```
Ejecutamos el algoritmo k_means
Ponemos 2 clusters ya que NbClust nos dice que el mejor numero de clusters es 2, pero en este caso puede ser 3 o 8 también una buena opción. Elegir el valor que convenga
```{r}
kmeans2 <- kmeans(df_aux,centers = 2,nstart = 25)
kmeans3 <- kmeans(df_aux,centers = 3,nstart = 25)
kmeans8 <- kmeans(df_aux,centers = 8,nstart = 25)
kmeans2
kmeans3
kmeans8
clusplot(pam(df_aux,2))
clusplot(pam(df_aux,3))
clusplot(pam(df_aux,8))
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
